\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{Vivek Sati} \\
\indent Email-id : \textbf{\url{gehurecruitviveksati@gmail.com}} \\
\indent Mobile No.: \textbf{+91 } \ \\
\indent \textbf{\url{https://github.com/Viveksati5143}}\\
\indent \textbf{\url{https://www.linkedin.com/in/vivek-sati/}}\\

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\
%\begin{table}[ht!]
%\begin{center}
\indent \rule{6.8in}{0.4pt}\\
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} }
\noindent \textbf{Year} & \textbf{Degree/Exam} & \textbf{Institute} & \textbf{GPA/Marks(\%)} \\
Aug, 2020 - Present & B.TECH in Computer Science & Graphic Era Hill University, Dehradun & $82.73 \%$ \\
2019 & $12^{th}$, \ C.B.S.E & Army Public School, Hempur & $80.00 \%$ \\

\end{tabular}
\indent \rule{6.8in}{0.4pt}
%\end{center}
%\end{table}
\\

\resheading{\textbf{EXPERIENCE} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0.5em}
\item \textbf{Web Development and Java Development Intern, Oasis Infobyte (Jan, 2023 - Feb, 2023) : }Developed
a Landing page for the company, Portfolio using HTML AND CSS, Temperature Converting Website using HTML, CSS and JAVASCRIPT; ATM Interface and Digital Library Management using Java.
The web portal was developed and uploaded to a Github repo.
\item \textbf{JGEC Winter of Code Mentee (Feb, 2023 - Mar, 2023) : }Contributed to different open source projects \& organizations on Github, gained experience on many Web development, ML, Python and other projects. Also, connected with people in the community from different places \& ranked among the top 20 contributors.
\end{itemize}

\resheading{\textbf{PROJECTS} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0.5em}
\item \textbf{Monitoring Dashboard for an application} (Apr, 2023 - May, 2023) : \\
\textit{Guide:\ Mrs. Lisa}\\
This project using nagios adds monitoring to an application by creating a dashboard. A feedback loop is added to help improve the quality of software such as code quality or usage metrics.

\item \textbf{Pipeline as a Code} (Mar, 2023 - Apr, 2023) : \\
Implemented a Jenkins Maven Project based on Pipeline as a Code and deployed the war file on tomcat server. It sends a Slack notification to the user on different stages of the pipeline whenever it gets triggered.

\item \textbf{Sentimental Analysis} (Oct, 2022 - Dec, 2022) : \\
\textit{Guide:\ Dr. Rakesh Patra}\\
Developed an ML project for recognizing sentiments using Logistic Regression giving $93\%$ accuracy. The python libraries used in this project are numpy, pandas, sklearn, matplotlib and NLTK.
\end{itemize} 

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0em}
\item \noindent \textbf{Languages} \textbf{Python}(Intermediate), \ \textbf{Java} (proficient), \ \textbf{C}, \ \textbf{HTML} (proficient), \ \textbf{CSS} (proficient), \ \textbf{SQL}
 \item \noindent\textbf{Tools and Frameworks} Bootstrap, \  \LaTeX\ , \ VS Code, \ IntelliJ IDEA, \ Eclipse IDE, \ Jupyter Notebook
\item \noindent \textbf{Machine Learning Tools} Pandas, \ Numpy, \ Sklearn, \ Matplotlib, \ NLTK
\item \noindent \textbf{DevOps} Git \& Github, \ Linux, \ Jenkins, \ Maven, \ Apache Tomcat, \ Selenium, \ Puppet, \ Docker, \ Ansible, \ Nagios, \ AWS
\end{itemize}

\resheading{\textbf{CERTIFICATIONS} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0em}
\item \noindent AWS Learning: Cloud Essentials
\item \noindent JGEC Winter of Code Mentee
\item \noindent Eddie Jaoude's Github Course

\end{itemize}

\resheading{\textbf{SCHOLASTIC \& CO-SCHOLASTIC ACHIEVEMENTS} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0em}
\item \noindent \textbf{The Checkmate Challengers - }Male head representative of the Chess Club in High school, April 2017
\item \noindent\textbf{Interschool sports meet - }1st runner up of badminton doubles in 2018
\item \noindent\textbf{Student Union - }Member of the student council, Part of many cleanliness and blood donation drives, \\ August 2018

\end{itemize}

\resheading{\textbf{POSITIONS OF RESPONSIBILITY} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0em}
\item \noindent \textbf{Discipline Incharge, Army Public School :} Gained efficient leadership skills through various stages and positions of responsibility
\item \noindent \textbf{CR ${2^{nd}}$ Sem (July, 2021) :}  Motivated and experienced in leading the class by being a diligent conveyor whilst maintaining the academic and social balance

\end{itemize}

\resheading{\textbf{STRENGTHS} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0em}
\item  Consistency, Leadership skills, Working under pressure, Team player and Goal oriented.

\end{itemize}
\end{document}